A Classical Density-Functional Theory for Describing Water Interfaces

### 2013-06-20 papers/water-saft/paper.tex
Added calculation and plot for X near a hydrophobic rod. Sarted on new water paper. Tested everything on node09.

\documentclass[twocolumn,amsmath,amssymb,prb]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/surface-tension}
\end{center}
\caption{Comparison of Surface tension versus temperature for theoretical and
  experimental data. The experimental data is taken from NIST.\cite{nistwater}
  The length-scaling parameter $\lscale$ is fit so that the theoretical surface 
  tension will match the experimental surface tension near room temperature.}
\label{fig:surface-tension}
\end{figure}

>>>>

\documentclass[twocolumn,amsmath,amssymb,prl]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\fixme{Some stuff about water}.  An important aspects of water is its
ability to form hydrogen bonds.  Each water molecule contains two
hydrogen bond donor sites and two acceptor sites.

\subsection{Statistical Associating Fluid Theory}

The SAFT Helmholtz free energy is composed of five terms:
\begin{equation} \label{eq:SAFT-free-energy}
  F = F_\textit{id} + F_\textit{hs} + F_\textit{disp} +
  F_\textit{assoc} + F_\textit{chain},
\end{equation}
where the first three terms---ideal gas, hard-sphere repulsion and
dispersion---encompass the \emph{monomer} contribution
to the free energy, the fourth is the \emph{association} free energy,
describing hydrogen bonds, and the final term is the chain formation
energy for fluids that are chain polymers. In our model, we use a hard
sphere reference fluid which renders $F_\textit{chain}$ irrelivant for
our functional.

In a recent paper \cite{hughes2013classical}, Hughes \emph{et al}
constructed a classical density functional theory for water which used
Clark \emph{et al}'s \cite{clark2006developing} five fitting
paramenters for an optimal cDFT for water.  In addition, they
introduced a parameter for the length scale over which the dispersion
interaction is correlated

\section{Method}

Schulte \emph{et al}\cite{schulte2012using} derived expressions for
the correlation fucntoin at contact based on the White Bear version of
FMT. They found their $g_{\sigma}^A$ to agree with Monte Carlo
simulation than Yu and Wu's which we was used in Hughes \emph{et al}'s
paper.  We use Hughs \emph{et al}'s functional and replace the
correlation with Schulte \emph{et al}'s, which we will call
$g_{\sigma}$. \fixme{expand this}.

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/surface-tension}
\end{center}
\caption{Comparison of Surface tension versus temperature for theoretical and
  experimental data. The experimental data is taken from NIST.\cite{nistwater}
  The length-scaling parameter $s_d$ is fit so that the theoretical surface 
  tension will match the experimental surface tension near room temperature.}
\label{fig:surface-tension}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/single-rod-X-plot}
\end{center}
\caption{ The average number of hydrogen bonding per molecule at
  distances from the center of a hydrophobic rod for various
  radii. The solid lines are the results from using the older
  $g_{\sigma}$, while the dotted lines are from Schulte \emph{et al}'s
  asymmetric $g_{\sigma}$.}
\label{fig:single-rod-X}
\end{figure}

\clearpage

\section{Introduction}

@@

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=3.5in]{figs/surface-tension}
%% \end{center}
%% \caption{Comparison of Surface tension versus temperature for theoretical and
%%   experimental data. The experimental data is taken from NIST.\cite{nistwater}
%%   The length-scaling parameter $\lscale$ is fit so that the theoretical surface 
%%   tension will match the experimental surface tension near room temperature.}
%% \label{fig:surface-tension}
%% \end{figure}
